Reanalysis Step 6: Sensitivity Analysis with E-values

### 2025-09-04 backup/reanalysis-6-sensitivity-interaction.qmd
data comparison

# Load results from previous steps
ps_results <- readRDS(file.path(reanalysis_data_dir, "ps_results_twang.rds"))

# Load outcome analysis results (from step 4)
outcome_results <- readRDS(file.path(reanalysis_data_dir, "outcome_analysis_results.rds"))
pooled_results <- outcome_results$pooled_coefficients
subgroup_effects <- outcome_results$subgroup_effects
```

@@

```{r overall-evalue}
# Extract the main lapse effect from pooled results
main_effect <- pooled_results[pooled_results$Term == "ever_lapse_binaryLapsed", ]

# Convert log odds to odds ratio
or_main <- exp(main_effect$Estimate)
ci_lower_main <- exp(main_effect$Estimate - 1.96 * main_effect$SE)
ci_upper_main <- exp(main_effect$Estimate + 1.96 * main_effect$SE)

@@

**Main Effect of Lapsing on Vision Impairment:**

@@

evalue_summary_main <- data.frame(
  Effect = "Main Effect (Lapsing)",
  OR = round(or_main, 3),
  CI_Lower = round(ci_lower_main, 3),
  CI_Upper = round(ci_upper_main, 3),
  E_Value_Point = round(evalue_point, 3),
  E_Value_CI = round(evalue_ci, 3)
)

@@

  # Get OR and CI
  or_val <- subgroup$OR
  ci_lower <- exp(subgroup$Log_Odds - 1.96 * subgroup$SE)
  ci_upper <- exp(subgroup$Log_Odds + 1.96 * subgroup$SE)

@@

# Extract coefficients for key confounders from the pooled model
benchmark_vars <- c("baseline_VA_logMAR", "CCI", "DCSI", "age_cat65-74", 
                   "gender_catMale", "insurance_catMedicare")

benchmark_effects <- pooled_results[pooled_results$Term %in% benchmark_vars, ]

@@

`r if(exists("max_measured_or")) paste0("**Strongest measured confounder OR:** ", round(max_measured_or, 2), "\n\n**Minimum E-value across subgroups:** ", round(min_evalue, 2), "\n\n**Interpretation:** ", if(min_evalue > max_measured_or) "Even the smallest E-value exceeds the strongest measured confounder, suggesting good robustness." else "Some E-values are comparable to measured confounders, suggesting potential sensitivity to unmeasured confounding of similar strength.") else ""`

>>>>

# Initialize logging
log_file <- init_log("sensitivity_analysis_interaction")

# Load outcome analysis results from interaction analysis
outcome_results <- readRDS(file.path(reanalysis_data_dir, "outcome_analysis_results.rds"))

# Extract the saved components
# pooled_coefficients is a list with odds_ratios, risk_differences, emmeans_list
pooled_results <- outcome_results$pooled_coefficients
subgroup_effects <- outcome_results$subgroup_effects  # This has the OR effects by subgroup
risk_differences <- outcome_results$risk_differences   # Risk differences on probability scale
```

@@

```{r overall-evalue}
# For interaction analysis, there's no single main effect
# Instead, we'll calculate an overall average effect across all subgroups
# This is a weighted average of the subgroup-specific effects

# Get the odds ratios from the subgroup effects
all_log_odds <- log(subgroup_effects$OR)
all_se <- subgroup_effects$SE  # SE is on log odds scale

# Calculate overall average effect (unweighted for simplicity)
# In practice, might want to weight by subgroup size
avg_log_odds <- mean(all_log_odds, na.rm = TRUE)
avg_se <- sqrt(mean(all_se^2, na.rm = TRUE))  # Root mean square of SEs

# Convert to OR scale
or_main <- exp(avg_log_odds)
ci_lower_main <- exp(avg_log_odds - 1.96 * avg_se)
ci_upper_main <- exp(avg_log_odds + 1.96 * avg_se)

@@

**Average Effect of Lapsing Across All Subgroups:**

@@

evalue_summary_main <- data.frame(
  Effect = "Average Effect Across Subgroups",
  OR = round(or_main, 3),
  CI_Lower = round(ci_lower_main, 3),
  CI_Upper = round(ci_upper_main, 3),
  E_Value_Point = round(evalue_point, 3),
  E_Value_CI = round(evalue_ci, 3)
)

@@

  # Get OR and CI (subgroup_effects already has OR, OR_CI_Lower, OR_CI_Upper)
  or_val <- subgroup$OR
  ci_lower <- subgroup$OR_CI_Lower
  ci_upper <- subgroup$OR_CI_Upper

@@

# For interaction analysis, we don't have main effect coefficients for confounders
# Instead, we'll note that benchmarking is not directly applicable
# since the interaction model focuses on subgroup-specific effects
benchmark_effects <- data.frame()

@@

**Note:** Benchmarking against measured confounders is not directly applicable in this interaction analysis, as we focus on subgroup-specific treatment effects rather than main effects of confounders.

**Minimum E-value across subgroups:** `r round(min_evalue, 2)`

**Interpretation:** `r if(min_evalue > 2) "The minimum E-value suggests good robustness to unmeasured confounding." else if(min_evalue > 1.5) "The minimum E-value suggests moderate robustness to unmeasured confounding." else "Some subgroups may be sensitive to unmeasured confounding."`
